---
title: "merging_datasets"
author: "Laura Menicacci"
date: "2022-11-25"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(countrycode)
library(readr)
```

## Loading datasets

```{r}
iea <- read_csv("policies_database_IEA_comma_utf8.csv")
eea <- read_csv("eea.csv") # to be updated
cpd <- read_csv("cpd.csv")
unfccc <- read_csv("unfccc_final.csv")
nc_links <- read_csv("C:/Users/laura/OneDrive/Documenti/LAURA/MCC/Policy databases/nc_links.csv")
```

# UNFCCC merging with NC links
```{r}
# pivot longer of nc links 
link_longer <- nc_links %>% 
  select(!"...1") %>% 
  pivot_longer(cols = c('NC1', 'NC2', 'NC3', 'NC4', 'NC5', 'NC6', 'NC7'), names_to = ('Source NC#'), values_to = ('Link'))

# left join
unfccc_new <- unfccc %>% 
  left_join(link_longer, by = c("Source NC#", "Country" = "country")) %>% 
  select(!"Link.x") %>% 
  rename(Link = Link.y)
```


# Datasets preparation

- filter for electricity sector
- filter for variables of interest: name of policy, policy description, years information, url to original policy
- add indicator database source column
```{r}
eea_prep <- eea %>% 
  filter(grepl(c("Energy Supply|Other Sectors"), `Sector(s) affected`)) %>% 
  select(Country, `Name of policy or measure`, Description, `Implementation period start`, `Implementation period finish`, `URL to main reference`) %>% 
  mutate(country_code = countrycode(Country, origin = "country.name", destination = "iso3c")) %>% 
  mutate(indicator_database_source = "EEA")

cpd_prep <- cpd %>% 
  select(Country, `Country ISO`, `Policy Title`, `Policy description`, `Date of decision`, `Start date of implementation`, `End date of implementation`,  `Source or references`) %>% 
  mutate(indicator_database_source = "Climate Policy Database")

iea_prep <- iea %>% 
  filter(grepl(c("Power, Heat and Utilities|Power generation|Electricity and heat generation|Combined heat and power"), Sectors)) %>% 
  select(Country, Year, Policy, Description, URL) %>% 
  mutate(country_code = countrycode(Country, origin = "country.name", destination = "iso3c")) %>%
  mutate(indicator_database_source = "IEA")

unfccc_prep <- unfccc_new %>% 
  select(Country, `Country Code`, `Source NC#`, Year, `Policy Name`, `Policy Description`, Link) %>% 
  mutate(year_implementation = NA) %>% 
  mutate(year_decision = NA) %>% 
  mutate(year_end = NA) %>% 
  mutate(indicator_database_source = "UNFCCC National Communications")
  
```

# Merge 
```{r}

unfccc_cpd <- full_join(unfccc_prep, cpd_prep, by = c("Country", "Country Code" = "Country ISO", "Policy Name" = "Policy Title", "Policy Description" = "Policy description", "year_implementation" = "Start date of implementation", "year_decision" = "Date of decision","year_end" = "End date of implementation",  "Link" = "Source or references", "indicator_database_source" ))

unfccc_cpd_eea <- full_join(unfccc_cpd, eea_prep, by = c("Country", "Country Code" = "country_code", "Policy Name" = "Name of policy or measure", "Policy Description" = "Description", "year_implementation" = "Implementation period start", "year_end" = "Implementation period finish",  "Link" = "URL to main reference", "indicator_database_source"))

unfccc_cpd_eea_iea <- full_join(unfccc_cpd_eea, iea_prep, by = c("Country", "Country Code" = "country_code", "Policy Name" = "Policy", "Policy Description" = "Description", "year_implementation" = "Year", "Link" = "URL", "indicator_database_source"))

```


# rename columns 
```{r}
ceres <- unfccc_cpd_eea_iea %>% 
  rename(year = Year) %>% 
  rename(country = Country) %>% 
  rename(country_code = "Country Code") %>% 
  rename(policy_name = "Policy Name") %>% 
  rename(policy_description = "Policy Description")
```


# Filter for all countries of interest are present

Australia, Austria, Belgium, Canada, Denmark, Finland, France, Germany, Greece, Ireland, Italy, Japan, Luxembourg, Netherlands, New Zealand, Portugal, Spain, Sweden, Switzerland, United Kingdom and the USA
```{r}
ceres_filtered <- ceres %>%
  filter(country_code %in% c("AUS", "AUT","BEL", "CAN", "DNK", "FIN", "FRA", "DEU", "GRC",
                      "IRL", "ITA", "JPN", "LUX", "NLD", "NZL", "PRT", "ESP", "SWE",
                      "CHE", "GBR", "USA"))
```


# Move NCnumber to source
```{r}
ceres_filtered <- cbind(ceres_filtered, indicator_database_source_1 =NA)

for(i in 1:nrow(ceres_filtered)){
  if(ceres_filtered[i,11]== 'UNFCCC National Communications'){
    ceres_filtered[i,12] = paste(ceres_filtered[i,11],ceres_filtered[i,3],sep = ' ')
  } else{
    ceres_filtered[i,12] =ceres_filtered[i,11]
}
}

ceres_final <- ceres_filtered %>% 
  select(!indicator_database_source) %>% 
  select(!`Source NC#`) %>% 
  rename(indicator_database_source = indicator_database_source_1)

```


```{r}
write_csv(ceres_final,"C:\\Users\\laura\\OneDrive\\Documenti\\LAURA\\MCC\\Policy databases\\ceres_secondversion.csv")
```

# New version with UNFCCC links
```{r}
write.csv(unfccc_cpd_eea_iea,"C:\\Users\\laura\\OneDrive\\Documenti\\LAURA\\MCC\\futurelab_ceres\\Policy databases\\ceres_thirdversion.csv")
```

