---
title: "Patent data project: an overview of the data"
author: "Laura Menicacci"
date: "2023-10-23"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(viridis)
library(scales)
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(kableExtra)

df <- read_csv("D:\\Aggregated\\PATS_IPC_25102023154540606.csv") 

df_ccs <- read_csv("D:\\Aggregated\\PATS_IPC_3010_w_CCS.csv") # always remember to remove World


```

## Patents by technology 

Link: https://stats.oecd.org/index.aspx?queryid=29068#

Selected: 
 - Y02 
 - priority applications 
 - country of inventor’s residence

 - TYPE OF PATENTS: 
 "Total Patents"                                                                                    
 "Climate change mitigation technologies related to buildings"                                      
 "Climate change mitigation technologies related to energy generation, transmission or distribution"
 "Climate change mitigation technologies related to transportation"                                 
 "Climate change mitigation technologies in the production or processing of goods"    
 
 - PATENT OFFICES:
  "Patent applications to the EPO"          
  "Patent applications filed under the PCT"
  "Patent applications to the USPTO"       
  "IP5 Patent families"    

## Country coverage

Print list of present countries. Total countries: 100
```{r, echo=FALSE}
agg_df <- df %>% 
  filter(`Technology domains & IPC` == "Total Patents") %>% 
  # check other filters
  select(Country, Value) %>% 
  group_by(Country) %>% 
  summarise(tot_counts = sum(Value))

agg_df %>% 
  select(Country) %>% 
  kable(format = "html") %>% 
  kable_styling(bootstrap_options = c("hover", "responsive"), full_width = F, fixed_thead = T, position = "left") %>% 
  scroll_box(width = "300px", height = "400px")

```

### Print world map for detailed overview of country coverage:
```{r worldmap, echo=FALSE, fig.height=6, fig.width=12}

# ADD CHINA + HONG KONG TOGETHER
# Unique names of the rows you want to sum
row_name1 <- "Hong Kong, China"
row_name2 <- "China (People's Republic of)"

# Find the indices of the rows with the specific names
indices <- which(agg_df$Country %in% c(row_name1, row_name2))

# Create a new row with the sum
new_row <- data.frame(Country = "China", tot_counts = sum(agg_df[indices, 2]))

# Add the new row to the data frame
agg_df2 <- rbind(agg_df, new_row)

world <- map_data("world")

agg_df2 <- agg_df2 %>% # rename countries the same to left join w lat lon data
  filter(!Country %in% c(row_name1, row_name2)) %>% 
  mutate(Country = str_replace(Country, "United States", "USA")) %>% 
  mutate(Country = str_replace(Country, "Slovak Republik", "Slovakia")) %>% 
  mutate(Country = str_replace(Country, "United Kingdom", "UK")) %>% 
  mutate(Country = str_replace(Country, "Türkiye", "Turkey")) %>% 
  mutate(Country = str_replace(Country, "Korea", "South Korea")) %>% 
  mutate(Country = str_replace(Country, "Democratic People's Republic of South Korea", "North Korea"))
  
#world_names <- world %>% pull(region)
#
#oecd_names <- agg_df2 %>% pull(Country)
#
#setdiff(world_names,oecd_names)

world_oecd <- left_join(world, agg_df2, by = c("region" = "Country"))


p <- ggplot()
p + geom_polygon(data=world_oecd, 
          aes(x=long, y=lat, group=group, fill = tot_counts/1000), # to remove one order of magnitude
          color="white", linewidth = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 3000, 
                       breaks = seq(0, 6000, 500), 
                       limits = c(0, 6754.368)) +
  theme_bw() + ggtitle("More fine-grained")


```




## NAs?
```{r}

table(is.na(df$Value))

table(is.na(df$Time))

```

### Distribution
```{r, echo=FALSE}
df_ccs %>% 
  filter(`Patents Office & Patents Families` == "Patent applications filed under the PCT") %>% 
  filter(`Technology domains & IPC` == "Total Patents") %>% 
  filter(!(Country == "World")) %>% 
  ggplot(aes(x = Value)) +
  geom_histogram(binwidth = 1.0000, fill = "navy", colour = "black", alpha = 0.7) +
  #scale_x_continuous(limits = c(0.0000, 68696.7000))+ 
                     #breaks = c(0, 1000, 2000, 3000, 4000, 5000, 6000, 7000)) +
  #scale_y_continuous(limits = c(0, 750))+
  xlab("Patent count") +
  ylab("") +
  theme_bw()
```
```{r, echo=FALSE}
df %>% 
ggplot(aes(x = Value)) +
 geom_boxplot(outlier.color = "red") +
  xlab("Patent count") +
  ylab("") +
  theme_bw()
```

## Time coverage

```{r, fig.height=10, fig.width=15, echo=FALSE}
df_ccs %>% 
  filter((Country == "World")) %>% 
  filter(!(`Technology domains & IPC` == "Total Patents")) %>% 
  #filter(`Patents Office & Patents Families` == "Patent applications to the EPO") %>% 
  select(Country, Value, Time, `Patents Office & Patents Families`, `Technology domains & IPC`) %>% 
  group_by(Country) %>% 
  ggplot(aes(x = Time, y= Value, colour = `Technology domains & IPC`)) + 
  geom_line() +
  facet_wrap(~`Patents Office & Patents Families`, scales = "free") + 
  theme_bw() +
  theme(legend.position = "right") + ggtitle("Patent applications by Patenting Office + technology type")

#df %>% 
#  filter(`Technology domains & IPC` == "Total Patents") %>% 
#  filter(`Patents Office & Patents Families` == "Patent applications filed under the PCT") %>% 
#  select(Country, Value, Time) %>% 
#  group_by(Country) %>% 
#  ggplot(aes(x = Time, y= Value, colour = Country)) + 
#  geom_line() +
#  theme_bw() +
#  theme(legend.position = "none") + ggtitle("Patent applications filed under the PCT")
#
#df %>% 
#  filter(`Technology domains & IPC` == "Total Patents") %>% 
#  filter(`Patents Office & Patents Families` == "Patent applications to the USPTO") %>% 
#  select(Country, Value, Time) %>% 
#  group_by(Country) %>% 
#  ggplot(aes(x = Time, y= Value, colour = Country)) + 
#  geom_line() +
#  theme_bw() +
#  theme(legend.position = "none") + ggtitle("Patent applications to the USPTO")
#
#df %>% 
#  filter(`Technology domains & IPC` == "Total Patents") %>% 
#  filter(`Patents Office & Patents Families` == "IP5 Patent families") %>% 
#  select(Country, Value, Time) %>% 
#  group_by(Country) %>% 
#  ggplot(aes(x = Time, y= Value, colour = Country)) + 
#  geom_line() +
#  theme_bw() +
#  theme(legend.position = "none") + ggtitle("IP5 Patent families")

```

```{r,echo=FALSE,fig.height=5, fig.width=10}
df %>% 
  filter(`Technology domains & IPC` == "Total Patents") %>% 
  #filter(`Patents Office & Patents Families` == "Patent applications to the EPO") %>% 
  select(`Patents Office & Patents Families`, Value, Time) %>% 
  group_by(`Patents Office & Patents Families`, Time) %>% 
  summarise(tot_pats = sum(Value)) %>%
  ggplot(aes(x = Time, y= tot_pats, colour = `Patents Office & Patents Families`)) + 
  geom_line() +
  theme_bw() +
  theme(legend.position = "right") + ggtitle("Patent applications by Patenting Office")
```

### with CCS technologies
```{r,echo=FALSE,fig.height=5, fig.width=10}
df_ccs %>% 
  filter(!(Country == "World")) %>% 
  filter(`Technology domains & IPC` == "Total Patents") %>% 
  #filter(`Patents Office & Patents Families` == "Patent applications to the EPO") %>% 
  select(`Patents Office & Patents Families`, Value, Time) %>% 
  group_by(`Patents Office & Patents Families`, Time) %>% 
  summarise(tot_pats = sum(Value)) %>%
  ggplot(aes(x = Time, y= tot_pats, colour = `Patents Office & Patents Families`)) + 
  geom_line() +
  theme_bw() +
  theme(legend.position = "right") + ggtitle("Patent applications by Patenting Office, with CCS technologies")

```


```{r, fig.width=15, echo=FALSE, include=FALSE}
df_ccs %>% 
  filter(!(Country == "World")) %>% 
  filter(!(`Technology domains & IPC` == "Total Patents")) %>% 
  #filter(`Patents Office & Patents Families` == "Patent applications to the EPO") %>% 
  select(`Technology domains & IPC`, Value, Time) %>% 
  group_by(`Technology domains & IPC`, Time) %>% 
  summarise(tot_pats = sum(Value)) %>%
  ggplot(aes(x = Time, y= tot_pats, colour = `Technology domains & IPC`)) + 
  geom_line() +
  theme_bw() +
  theme(legend.position = "right") + ggtitle("Patent applications by technology, with CCS technologies")
```

```{r, fig.width=20}
#rd  <- read_csv("C:\\Users\\laura\\Downloads\\DP_LIVE_30102023130505034.csv")
#
#rd %>% pull(LOCATION) %>% unique() %>% length()
#
#rd %>% pull(LOCATION) %>% unique() 

df_ccs %>% 
  filter(!(Country == "World")) %>% 
  filter(!(`Technology domains & IPC` == "Total Patents")) %>% 
  #filter(`Patents Office & Patents Families` == "Patent applications to the EPO") %>% 
  filter(Country %in% c("Germany", "Japan", "United States", "China (People's Republic of)")) %>% 
  select(`Technology domains & IPC`, Country, Value, Time) %>% 
  group_by(`Technology domains & IPC`,Country, Time) %>% 
  summarise(tot_pats = sum(Value)) %>%
  ggplot(aes(x = Time, y= tot_pats, colour = `Technology domains & IPC`)) + 
  geom_line() +
  facet_wrap(~Country, scales = "fixed") + 
  theme_bw() +
  theme(legend.position = "right") + ggtitle("Patent applications by country")

```

# NUOVA PROVA 

https://stats.oecd.org/Index.aspx?DataSetCode=PAT_DEV#

```{r}
dat <- read_csv("D:\\Aggregated\\PAT_DEV_01112023143241837.csv")

# cambia palette

dat %>% 
  filter((`Inventor country` == "World")) %>% 
  select(`Technology domain`, Value, Year) %>% 
  group_by(`Technology domain`, Year) %>% 
  summarise(tot_pats = sum(Value)) %>%
  ggplot(aes(x = Year, y= tot_pats, colour = `Technology domain`)) + 
  geom_line() +
  #facet_wrap(~Country, scales = "fixed") + 
  scale_x_continuous(limits = c(1960, 2019))+
  theme_bw() +
  theme(legend.position = "right") + ggtitle("Patent applications by Y02E10 technology: Renewable energy generation")
  
```
## MAP with new dataset 
```{r, fig.width=20}

agg_dat <- dat %>% 
  #filter(`Technology domains & IPC` == "Total Patents") %>% 
  # check other filters
  rename("Inventor_country" = "Inventor country") %>% 
  select(Inventor_country, Value) %>% 
  group_by(Inventor_country) %>% 
  summarise(tot_counts = sum(Value))

agg_dat2 <- agg_dat[-151,] # remove world count

# ADD CHINA + HONG KONG + MACAU COUNT TOGETHER
# Unique names of the rows you want to sum
row_name1 <- "Hong Kong, China"
row_name2 <- "China (People's Republic of)"
row_name3 <- "Macau, China"

# Find the indices of the rows with the specific names
indices <- which(agg_dat2$Inventor_country %in% c(row_name1, row_name2, row_name3))

# Create a new row with the sum
new_row <- data.frame(Inventor_country = "China", tot_counts = sum(agg_dat2[indices, 2]))

# Add the new row to the data frame
agg_dat3 <- rbind(agg_dat2, new_row)

# Remove old rows
agg_dat3 <- agg_dat3[-indices,]


world <- map_data("world") # latitude and longitude data

# rename countries the same to left join w lat lon data
agg_dat4 <- agg_dat3 %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "United States", "USA")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Slovak Republic", "Slovakia")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "United Kingdom", "UK")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Türkiye", "Turkey")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Korea", "South Korea")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Democratic People's Republic of South Korea", "North Korea")) %>%
  mutate(Inventor_country = str_replace(Inventor_country, "Palestinian Authority or West Bank and Gaza Strip", "Palestine")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Viet Nam", "Vietnam")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Brunei Darussalam", "Brunei")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Chinese Taipei", "Taiwan")) %>% 
mutate(Inventor_country = str_replace(Inventor_country, "Faeroe Islands", "Faroe Islands")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Lao People's Democratic Republic", "Laos")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Réunion", "Reunion")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Saint Vincent and the Grenadines", "Saint Vincent")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Syrian Arab Republic", "Syria"))
  
  
#world_names <- world %>% pull(region)
#
#oecd_names <- agg_df2 %>% pull(Country)
#
#setdiff(world_names,oecd_names)

world_oecd <- left_join(world, agg_dat4, by = c("region" = "Inventor_country"))


p <- ggplot()
p + geom_polygon(data=world_oecd, 
          aes(x=long, y=lat, group=group, fill = tot_counts),
          color="white", linewidth = 0.2) + 
  #scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
  #                     midpoint = 3000, 
  #                     breaks = seq(0, 6000, 500), 
  #                     limits = c(0, 6754.368)) +
  #
  theme_bw() 

```

# Focus on renewable energy technologies 
```{r}
agg_tech <- dat %>% 
  #filter(`Technology domains & IPC` == "Total Patents") %>% 
  rename("Inventor_country" = "Inventor country") %>% 
  rename("Technology" = "Technology domain") %>% 
  select(Inventor_country, Technology, Value) %>% 
  group_by(Inventor_country, Technology) %>% 
  summarise(tot_counts = sum(Value))

# add row for each technology for each country 
tech_types <- dat %>% pull(`Technology domain`) %>% unique()
countries <- dat %>% pull(`Inventor country`) %>% unique()
count <- 0
 
new_agg_tech <- data.frame(
    Inventor_country = rep(countries, each = length(tech_types)),
    Technology = rep(tech_types, times = length(countries))
)

agg_tech1 <- left_join(new_agg_tech, agg_tech, by = c("Inventor_country", "Technology")) %>% 
    mutate_if(is.numeric, funs(ifelse(is.na(.), 0, .)))

##############################

agg_tech2 <- agg_tech1 %>% filter(!(Inventor_country == "World")) # remove world count

# ADD CHINA + HONG KONG + MACAU COUNT TOGETHER
# Unique names of the rows you want to sum
row_name1 <- "Hong Kong, China"
row_name2 <- "China (People's Republic of)"
row_name3 <- "Macau, China"

# ADD STEP: SUM OVER TECHNOLOGY TYPES
col_list <- c(row_name1, row_name2, row_name3)

china <- agg_tech2 %>% 
  filter(Inventor_country %in% col_list) %>% 
  pivot_wider(names_from = Inventor_country, values_from = tot_counts) %>% 
  replace(is.na(.), 0) %>%
  rowwise() %>% 
  mutate(China = sum(c_across(all_of(col_list)))) %>% 
  select(!(col_list)) %>% 
  pivot_longer(cols = "China", names_to = "Inventor_country", values_to = "tot_counts")

# Add the new row to the data frame
agg_tech3 <- rbind(agg_tech2, china)

# Remove old rows
indices <- which(agg_tech3$Inventor_country %in% c(row_name1, row_name2, row_name3))

agg_tech3 <- agg_tech3[-indices,]

world <- map_data("world") # latitude and longitude data

# rename countries the same to left join w lat lon data
agg_tech4 <- agg_tech3 %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "United States", "USA")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Slovak Republic", "Slovakia")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "United Kingdom", "UK")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Türkiye", "Turkey")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Korea", "South Korea")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Democratic People's Republic of South Korea", "North Korea")) %>%
  mutate(Inventor_country = str_replace(Inventor_country, "Palestinian Authority or West Bank and Gaza Strip", "Palestine")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Viet Nam", "Vietnam")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Brunei Darussalam", "Brunei")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Chinese Taipei", "Taiwan")) %>% 
mutate(Inventor_country = str_replace(Inventor_country, "Faeroe Islands", "Faroe Islands")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Lao People's Democratic Republic", "Laos")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Réunion", "Reunion")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Saint Vincent and the Grenadines", "Saint Vincent")) %>% 
  mutate(Inventor_country = str_replace(Inventor_country, "Syrian Arab Republic", "Syria"))
  

```


# Plot patent count by tech type
```{r, fig.height=15, fig.width=20}
world_oecd_tech <- left_join(world, agg_tech4, by = c("region" = "Inventor_country")) %>% drop_na(Technology)

p <- ggplot()
p + geom_polygon(data=world_oecd_tech, 
          aes(x=long, y=lat, group=group, fill = tot_counts), # to remove one order of magnitude
          color="white", linewidth = 0.2) + 
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", 
                       midpoint = 8000,  # mean
                       breaks = seq(0, 16000, 1500), 
                       limits = c(0, 16108.99)) +
  facet_wrap(~Technology) +
  theme_bw() + 
  ggtitle("By Y02E10 technology")


```

