---
title: "sc_replication_more_specs"
author: "Laura Menicacci"
date: "2024-01-24"
output: html_document
---

# Generalised synthetic controls replication {.tabset}

Results refer to the following specification: 

 * Y: Log count +1
 * Controls: lgdp + lpop
 * Sample: top 25 patenting countries by mean - CCMT technologies
 * AR(1)
 * IIS = ON
 * p-value = 0.01 

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load Libraries
suppressWarnings(suppressMessages(library(knitr)))
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(gsynth)))
suppressWarnings(suppressMessages(library(panelView)))
suppressWarnings(suppressMessages(library(patchwork)))
suppressWarnings(suppressMessages(library(gets)))
suppressWarnings(suppressMessages(library(getspanel)))
suppressWarnings(suppressMessages(library(kableExtra)))

top_25 <- c("JPN", "USA", "KOR", "DEU", "CHN", "FRA", "GBR", "TWN", "CAN", "ITA", "DNK", "NLD", "IND", "AUT", "CHE", "SWE", "ESP", "AUS", "ISR", "BEL", "FIN", "RUS", "NOR", "SGP", "BRA")

# Load Data
#data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = #F) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% #mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop))
#

## for preferred spec: top_25 and log transformation 
res_w_breaks <- readRDS(".\\prefe_results_w_breaks_list_09_01.RDS")

#1) the pre-treatment fit: it should be flat, ideally (remember that for all pre-treatment periods, scm #essentially works as some kind of, in the gsynth case very complicated, matching-type procedure. the #pre-treatment counterfactual should be very close to the pre-treatment factual. for all post-treatment #periods, scm essentially works as some out-of sample prediction method, nothing causal to look at here #really, in a strict sense)
#2) whether i actually see some (persistent) effect in the right direction (this is not always the case, see #e.g. oecd buildings
#3) then at the confidence interval

```

# CCMT

0) Original "baseline" model
1) EM = TRUE in the argument 
2) inference = "jackknife" 
3) estimator = "mc" 

Countries with treatment before 2000 cannot be estimated (India). 

List of breaks:

```{r, echo=FALSE}
data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = F, col_names = T) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop)) %>% filter(tech == "Climate change mitigation")
# list of breaks for ccmt

res_w_breaks %>% 
  filter(tech == "ccmt" & p_val == 0.01) %>% 
  pull(breaks)

# Create Staggered SCM Treatments with list of breaks

data$treated <- 0

# pval 0.01
data$treated <- ifelse(data$ISO == "AUS" & data$year >= 2005, 1, data$treated)
data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2005, 1, data$treated)
#data$treated <- ifelse(data$ISO == "IND" & data$year >= 1998, 1, data$treated)
data$treated <- ifelse(data$ISO == "IND" & data$year >= 2000, 1, data$treated)
data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2003, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2005, 1, data$treated)

# pval 0.05
#data$treated <- ifelse(data$ISO == "AUS" & data$year >= 2005, 1, data$treated)
#data$treated <- ifelse(data$ISO == "CAN" & data$year >= 1997, 1, data$treated)
#data$treated <- ifelse(data$ISO == "CHN" & data$year >= 2001, 1, data$treated)
##data$treated <- ifelse(data$ISO == "CHN" & data$year >= 2015, 1, data$treated)
#data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2005, 1, data$treated)
##data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2006, 1, data$treated)
##data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2007, 1, data$treated)
#data$treated <- ifelse(data$ISO == "IND" & data$year >= 1998, 1, data$treated)
##data$treated <- ifelse(data$ISO == "IND" & data$year >= 2000, 1, data$treated)
#data$treated <- ifelse(data$ISO == "ISR" & data$year >= 2009, 1, data$treated)
#data$treated <- ifelse(data$ISO == "RUS" & data$year >= 1998, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2003, 1, data$treated)
##data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2005, 1, data$treated)
#data$treated <- ifelse(data$ISO == "TWN" & data$year >= 2001, 1, data$treated)


# Check Treatments
v1 <- panelview(count ~ treated, data = data,  
          index = c("ISO","year"), 
          pre.post = TRUE,
          axis.adjust = TRUE,
          cex.axis.y = 8, 
          cex.legend = 8, 
          background = "white") 

# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "parametric", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)

#saveRDS(out, file = ".\\gsynth_ccmt.RDS")

```

## Basic specification {.tabset}


### Positive {.tabset}


```{r ccmt-plot-pos, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt.RDS")

plot(out, type = "gap", id = "DNK", main = "Denmark 2005 (Climate change mitigation)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2005 (Climate change mitigation)")

plot(out, type = "gap", id = "IND", main = "India 2000 (Climate change mitigation)")
plot(out, type = "ct", id = "IND", main = "India 2000 (Climate change mitigation)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2003 (Climate change mitigation)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2003 (Climate change mitigation)")

```


### Negative {.tabset}


```{r ccmt-plot-neg, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt.RDS")

plot(out, type = "gap", id = "AUS", main = "Australia 2005 (Climate change mitigation)")
plot(out, type = "ct", id = "AUS", main = "Australia 2005 (Climate change mitigation)")

```


## EM method {.tabset}

```{r, echo=FALSE}
# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), EM = TRUE, force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "parametric", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)

#saveRDS(out, file = ".\\gsynth_ccmt_EM_true.RDS")

```




### Positive {.tabset}


```{r ccmt-plot-pos-em, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_EM_true.RDS")

plot(out, type = "gap", id = "DNK", main = "Denmark 2005 (EM Method)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2005 (EM Method)")

plot(out, type = "gap", id = "IND", main = "India 2000 (EM Method)")
plot(out, type = "ct", id = "IND", main = "India 2000 (EM Method)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2003 (EM Method)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2003 (EM Method)")

```


### Negative {.tabset}


```{r ccmt-plot-neg-em, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_EM_true.RDS")

plot(out, type = "gap", id = "AUS", main = "Australia 2005 (EM Method)")
plot(out, type = "ct", id = "AUS", main = "Australia 2005 (EM Method)")

```


## Jackknife method {.tabset}

```{r, echo=FALSE}
# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "jackknife", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)

#saveRDS(out, file = ".\\gsynth_ccmt_jackknife.RDS")

```




### Positive {.tabset}


```{r ccmt-plot-pos-jackknife, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_jackknife.RDS")

plot(out, type = "gap", id = "DNK", main = "Denmark 2005 (jaccknife method)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2005 (jaccknife method)")

plot(out, type = "gap", id = "IND", main = "India 2000 (jaccknife method)")
plot(out, type = "ct", id = "IND", main = "India 2000 (jaccknife method)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2003 (jaccknife method)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2003 (jaccknife method)")

```


### Negative {.tabset}


```{r ccmt-plot-neg-jackknife, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_jackknife.RDS")

plot(out, type = "gap", id = "AUS", main = "Australia 2005 (jaccknife method)")
plot(out, type = "ct", id = "AUS", main = "Australia 2005 (jaccknife method)")

```


## MC (matrix completion) method {.tabset}

Change boostrap to nonparametric to run this specification. 

```{r, echo=FALSE}
# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, estimator = "mc",
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "nonparametric", nboots = 1000, 
#                parallel = FALSE)
#)
#
#saveRDS(out, file = ".\\gsynth_ccmt_estimator_mc.RDS")

```


### Positive {.tabset}


```{r ccmt-plot-pos-mc, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_estimator_mc.RDS")

plot(out, type = "gap", id = "DNK", main = "Denmark 2005 (mc estimator)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2005 (mc estimator)")

plot(out, type = "gap", id = "IND", main = "India 2000 (mc estimator)")
plot(out, type = "ct", id = "IND", main = "India 2000 (mc estimator)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2003 (mc estimator)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2003 (mc estimator)")

```


### Negative {.tabset}


```{r ccmt-plot-neg-mc, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_estimator_mc.RDS")

plot(out, type = "gap", id = "AUS", main = "Australia 2005 (mc estimator)")
plot(out, type = "ct", id = "AUS", main = "Australia 2005 (mc estimator)")

```

## EM & jackknife {.tabset}

```{r em-jack, echo=F}

# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"),  EM = TRUE, force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "jackknife", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)
#saveRDS(out, file = ".\\gsynth_ccmt_jackknife_em.RDS")

```

### Positive {.tabset}


```{r ccmt-plot-pos-jackknife-em, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_jackknife_em.RDS")

plot(out, type = "gap", id = "DNK", main = "Denmark 2005 (jaccknife & EM method)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2005 (jaccknife & EM method)")

plot(out, type = "gap", id = "IND", main = "India 2000 (jaccknife & EM method)")
plot(out, type = "ct", id = "IND", main = "India 2000 (jaccknife & EM method)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2003 (jaccknife & EM method)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2003 (jaccknife & EM method)")

```

### Negative {.tabset}


```{r ccmt-plot-neg-jackknife-em, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt_jackknife_em.RDS")

plot(out, type = "gap", id = "AUS", main = "Australia 2005 (jaccknife & EM method)")
plot(out, type = "ct", id = "AUS", main = "Australia 2005 (jaccknife & EM method)")

```