---
title: "setup_model"
author: "Laura Menicacci"
date: "2023-12-05"
output: html_document
---

# Exploration Break detection

-   Controls: GDP and population
-   Data samples: Y02(all ccmts), Y02E (energy), solar, wind, batteries
-   Country sample:

Specifications:

-   levels
-   levels + AR(1)
-   IIS on & off
-   p-values (0.05, 0.01)
-   growth rates
-   growth rates + AR(1)
-   IIS on & off
-   p-values (0.05, 0.01)

```{r}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(readxl)
library(gdata)
library(ggthemes)
library(collapse)
library(plm)
library(forecast)
library(tseries)
library(patchwork)

# carica dataset
```

## Histogram & boxplot

```{r, echo=FALSE, fig.height=10, fig.width=15}
stats_pat <- df2 %>% 
  group_by(ISO, tech) %>% 
  summarise(median = median(count, na.rm=TRUE),
            q25 = quantile(count, 0.25),
            mean = mean(count, na.rm=TRUE), 
            q75 = quantile(count, 0.75), 
            max = max(count, na.rm=TRUE), 
            sd = sd(count, na.rm=TRUE), .groups = "keep")

box <- stats_pat %>% 
  ggplot(aes(x = mean))+ 
  geom_boxplot(colour = "black", outlier.colour = "red", size = 0.5) +
  #geom_vline(xintercept = quantile(stats_pat$mean, 0.3), color = "red")+
  facet_wrap(~tech, scales = "free") + 
  xlab("")+
  ylab("mean patent counts by country") +
  theme_clean() +
  theme(plot.background = element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

hist <- stats_pat %>% 
  ggplot(aes(x = mean)) +
  geom_histogram(binwidth = 1, fill = "navy", colour = "black", alpha = 0.7) +
  facet_wrap(~tech, scales = "free") + 
  ylab("") +
  xlab("mean patent counts by country (binwidth = 1)") +
  theme_clean() +
  theme(plot.background = element_blank())

box / hist

```

## Restrict country sample

1. Group by country and technology class 

2. Create statistical info: median, q25, mean, q75, max sd

3. Selection criteria: if q25 of country&tech is less than q30 of entire distribution: drop 

4. Total sample: 21 countries 

Reasons:

* I wanted to make sure that all countries in the sample had a decent distribution for all the technologies for the first run of the model
* For a first run: keep sample small to make it run faster
* Double-checked with *top 25 patenting countries*: they are the same, I only excluded Brazil, India, Taiwan, Singapore (reason for this: they have less patents in one of the narrow technologies), which then were added for the second run 


```{r}
#q30 <- quantile(df2$count, 0.30)
#
#nonpat_q30 <- c() # 175
#
#
#for (i in 1:nrow(stats_pat)){
#  if (stats_pat[i, 4] <= q30[[1]]){ # if q25 of country&tech is less than q30 of entire #distribution: drop
#    nonpat_q30 <- append(nonpat_q30, stats_pat[[i, 1]]) 
#                       }
#}
#
#df_strict <- df2 %>% filter(!(ISO %in% nonpat_q30))

```


```{r, echo=FALSE, fig.height=20, fig.width=15}

#stats_pat %>% 
#  group_by(tech) %>% 
#  arrange(desc(mean))

stats_pat2 <- stats_pat[order(stats_pat$mean, decreasing = TRUE),]

top_pat_countries <- unique(stats_pat2[1:156, 1]) # top 50 patenting countries 

df3 <- df2 %>% filter(ISO %in% top_pat_countries$ISO)

stats_pat_top <- df3 %>% 
  group_by(ISO, tech) %>% 
  summarise(median = median(count, na.rm=TRUE),
            q25 = quantile(count, 0.25),
            mean = mean(count, na.rm=TRUE), 
            q75 = quantile(count, 0.75), 
            max = max(count, na.rm=TRUE), 
            sd = sd(count, na.rm=TRUE), 
            tot = sum(count, na.rm = TRUE), .groups = "keep")

box <- stats_pat_top %>% 
  ggplot(aes(x = mean))+ 
  geom_boxplot(colour = "black", outlier.colour = "red", size = 0.5) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red")+
  facet_wrap(~tech, scales = "free") + 
  xlab("")+
  ylab("mean patent counts by country") +
  theme_clean() +
  theme(plot.background = element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

hist <- stats_pat_top %>% 
  ggplot(aes(x = mean)) +
  geom_histogram(binwidth = 1, fill = "navy", colour = "black", alpha = 0.7) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red") +
  facet_wrap(~tech, scales = "free") + 
  ylab("") +
  xlab("mean patent counts by country (binwidth = 1)") +
  theme_clean() +
  theme(plot.background = element_blank())

line <- df3 %>% 
  group_by(tech, year) %>%
  summarise(tot = sum(count), .groups = "keep") %>% 
  ggplot(aes(y = tot, x = year)) +
  geom_line(colour = "black", alpha = 0.7) +
  facet_wrap(~tech, scales = "free") + 
  ylab("aggregated patent counts by tech") +
  xlab("year") +
  theme_clean() +
  theme(plot.background = element_blank())

box / hist / line

```

## Add here time series analysis

-   check for stationarity by technology
-   take in case differenced mean ?

```{r, echo=TRUE}

adf_data_ccmt <- df3 %>% filter(tech == "Climate change mitigation")

adf_data_energy <- df3 %>% filter(tech == "Climate change mitigation technologies related to energy generation, transmission or distribution")

adf_data_batteries <- df3 %>% filter(tech == "Batteries")

adf_data_solar <- df3 %>% filter(tech == "Solar energy")

adf_data_wind <- df3 %>% filter(tech == "Wind energy")


library(urca)

############################# CCMT

summary(ur.df(y=adf_data_ccmt$count, type = "none",lags=1))

summary(ur.df(y=adf_data_ccmt$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_ccmt$count, type = "trend",lags=1))
```

```{r}
############################# ENERGY

summary(ur.df(y=adf_data_energy$count, type = "none",lags=1))

summary(ur.df(y=adf_data_energy$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_energy$count, type = "trend",lags=1))
```

```{r}
########################### SOLAR

summary(ur.df(y=adf_data_solar$count, type = "none",lags=1))

summary(ur.df(y=adf_data_solar$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_solar$count, type = "trend",lags=1))
```

```{r}
########################## WIND

summary(ur.df(y=adf_data_wind$count, type = "none",lags=1))

summary(ur.df(y=adf_data_wind$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_wind$count, type = "trend",lags=1))
```

```{r}
######################### BATTERIES

summary(ur.df(y=adf_data_batteries$count, type = "none",lags=1))

summary(ur.df(y=adf_data_batteries$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_batteries$count, type = "trend",lags=1))
```


## Create logs

```{r, echo=FALSE, include=FALSE}
df_mod <- df3 %>% 
  mutate(lpop = log(pop), # log pop
         lgdp = log(gdp), # log gdp
         lgdp_sq = log(gdp)^2, # squared gdp
         log_count = log(count+1)) # log+1 transformation

df_mod %>% pull(ISO) %>% unique # sanity check

df_mod %>% filter(!complete.cases(.)) # Israel does not have GDP for all years (1990-1994 are missing)

df_mod <- df_mod %>% drop_na()

```

## Load samples for different techs & create growth rates

```{r, echo=FALSE, include=FALSE}
techs <- c("Climate change mitigation", "Climate change mitigation technologies related to energy generation, transmission or distribution", "Batteries", "Wind energy", "Solar energy")

ccmt <- df_mod %>% filter(tech == "Climate change mitigation")

pgr <- pdata.frame(ccmt, index = c("ISO","year")) 

ccmt$count_gr <- G(pgr$count, n = 1) 
ccmt$pop_gr <- G(pgr$pop, n = 1) 
ccmt$gdp_gr <- G(pgr$gdp, n = 1) 

ccmt <- ccmt %>% mutate(count_ma = ma(count_gr,3), 
                        pop_ma = ma(pop_gr,3), 
                        gdp_ma = ma(gdp_gr,3)) %>% 
  drop_na() %>% 
  filter(year > 1994)

ccmt %>% filter(!complete.cases(.))

ccmt1 <- make.pbalanced(ccmt)

is.pbalanced(ccmt1)

########################

```

# Functional forms

```{r, echo=FALSE, include=FALSE}
controls <- c("~ gdp + pop", "~ lgdp + lpop", "~ gdp_ma + pop_ma") # specify controls 

dep_var <- c("count", "log_count", "count_ma") # specify dependent var  

base_forms <- paste0(dep_var, controls) # paste together

base_forms

```

# Analysis: CCMT

```{r, echo=FALSE, include=FALSE}

cl <- makeCluster(6) 
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- ccmt1
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = TRUE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(ccmt1$year),":",max(ccmt1$year)), # time series
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = TRUE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl) # stop parallelizing 

saveRDS(models, ".\\ccmt_IIS.RDS")  # save model output 
```

## Analysis: no IIS

```{r, echo=FALSE, include=FALSE}
cl <- makeCluster(6)
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- ccmt1
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = FALSE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(ccmt1$year),":",max(ccmt1$year)), # time series
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = FALSE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl) # stop parallelizing 

saveRDS(models, ".\\ccmt_noIIS.RDS")
```

## Energy

```{r, echo=FALSE, include=FALSE}

energy <- df_mod %>% filter(tech == "Climate change mitigation technologies related to energy generation, transmission or distribution")

pgr <- pdata.frame(energy, index = c("ISO","year")) 

energy$count_gr <- G(pgr$count, n = 1) 
energy$pop_gr <- G(pgr$pop, n = 1) 
energy$gdp_gr <- G(pgr$gdp, n = 1) 

energy <- energy %>% mutate(count_ma = ma(count_gr,3), 
                        pop_ma = ma(pop_gr,3), 
                        gdp_ma = ma(gdp_gr,3)) %>% 
  drop_na() %>% 
  filter(year > 1994)

energy %>% filter(!complete.cases(.))

energy1 <- make.pbalanced(energy)

is.pbalanced(energy1)

################# model w IIS

cl <- makeCluster(6) 
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- energy1
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = TRUE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(energy1$year),":",max(energy1$year)), # time series
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = TRUE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl)

saveRDS(models, ".\\energy_IIS.RDS")  # save model output 

################################ NO IIS

cl <- makeCluster(6)
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- energy1
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = FALSE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(energy1$year),":",max(energy1$year)), # time series
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = FALSE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl) # stop parallelizing 

saveRDS(models, ".\\energy_noIIS.RDS")
```

## Wind

```{r, echo=FALSE, include=FALSE}
wind <- df_mod %>% filter(tech == "Wind energy")  %>% 
  filter(year > 1994)

#pgr <- pdata.frame(wind, index = c("ISO","year")) 
#
#wind$count_gr <- G(pgr$count, n = 1) 
#wind$pop_gr <- G(pgr$pop, n = 1) 
#wind$gdp_gr <- G(pgr$gdp, n = 1) 
#
#wind <- wind %>% mutate(count_ma = ma(count_gr,3), 
#                        pop_ma = ma(pop_gr,3), 
#                        gdp_ma = ma(gdp_gr,3)) %>% 
#  drop_na()

wind %>% filter(!complete.cases(.))

#wind1 <- make.pbalanced(wind)

is.pbalanced(wind)

################# new controls

controls <- c("~ gdp + pop", "~ lgdp + lpop") # specify controls 

dep_var <- c("count", "log_count") # specify dependent var  

base_forms <- paste0(dep_var, controls) # paste together

################# model w IIS

cl <- makeCluster(6) 
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- wind
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = TRUE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(wind$year),":",max(wind$year)), # time series
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = TRUE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl)

saveRDS(models, ".\\wind_IIS.RDS")  # save model output 

################################ NO IIS

cl <- makeCluster(6)
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- wind
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = FALSE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(wind$year),":",max(wind$year)), 
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = FALSE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl) # stop parallelizing 

saveRDS(models, ".\\wind_noIIS.RDS")

```

## Solar

```{r, echo=FALSE, include=FALSE}
solar <- df_mod %>% filter(tech == "Solar energy")

pgr <- pdata.frame(solar, index = c("ISO","year")) 

solar$count_gr <- G(pgr$count, n = 1) 
solar$pop_gr <- G(pgr$pop, n = 1) 
solar$gdp_gr <- G(pgr$gdp, n = 1) 

solar <- solar %>% mutate(count_ma = ma(count_gr,3), 
                        pop_ma = ma(pop_gr,3), 
                        gdp_ma = ma(gdp_gr,3)) %>% 
  drop_na() %>% 
  filter(year > 1994)

solar %>% filter(!complete.cases(.))

solar1 <- make.pbalanced(solar)

is.pbalanced(solar1)

################# model w IIS

cl <- makeCluster(6) 
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- solar1
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = TRUE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(solar1$year),":",max(solar1$year)), # time series
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = TRUE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl)

saveRDS(models, ".\\solar_IIS.RDS")  # save model output 

################################ NO IIS

cl <- makeCluster(6)
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- solar1
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = FALSE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(solar1$year),":",max(solar1$year)), 
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = FALSE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl) # stop parallelizing 

saveRDS(models, ".\\solar_noIIS.RDS")

```

## Batteries

```{r, echo=FALSE, include=FALSE}

batteries <- df_mod %>% filter(tech == "Batteries") %>% 
  filter(year > 1994)

#pgr <- pdata.frame(batteries, index = c("ISO","year")) 
#
#batteries$count_gr <- G(pgr$count, n = 1) 
#batteries$pop_gr <- G(pgr$pop, n = 1) 
#batteries$gdp_gr <- G(pgr$gdp, n = 1) 
#
#batteries <- batteries %>% mutate(count_ma = ma(count_gr,3), 
#                        pop_ma = ma(pop_gr,3), 
#                        gdp_ma = ma(gdp_gr,3)) %>% 
#  drop_na()

batteries %>% filter(!complete.cases(.))

#batteries1 <- make.pbalanced(batteries)

is.pbalanced(batteries)

################# new controls

controls <- c("~ gdp + pop", "~ lgdp + lpop") # specify controls 

dep_var <- c("count", "log_count") # specify dependent var  

base_forms <- paste0(dep_var, controls) # paste together

################# model w IIS

cl <- makeCluster(6) 
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- batteries
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = TRUE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(batteries$year),":",max(batteries$year)), # time series
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = TRUE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl)

saveRDS(models, ".\\batteries_IIS.RDS")  # save model output 

################################ NO IIS

cl <- makeCluster(6)
registerDoParallel(cl)

models <- foreach(f = base_forms, .combine = rbind, .packages = c('tidyverse', 'getspanel')) %:% # specify functional form 
  #foreach(smpl = techs, .combine = rbind) %:% # specify samples
  foreach(a = c(0,1), .combine = rbind) %:%
  foreach(p.value = c(0.01, 0.05), .combine = rbind, .errorhandling = "remove") %dopar% {
    dat <- batteries
      is <- isatpanel( # main function
            data = dat,
            formula = as.formula(f),
            index = c("ISO", "year"), # id and time
            effect = "twoways", # twoway fixed effects chosen as estimator
            iis = FALSE, # enable impulse indicator saturation
            fesis = TRUE, # enable fixed effects indicator saturation
            ar = a, # specify auto-regressive terms
            t.pval = p.value,  # false positive rate
            max.block.size = 20 # size for block search 
            )
          models = tibble(source = f, 
                          #state_sample = smpl,    # which sample 
                          year_range = paste0(min(batteries$year),":",max(batteries$year)), 
                          p_val = p.value, # false positive rates 
                          is = list(is), # model
                          iis = FALSE, # IIS
                          b_size = 20,
                          ar = a)
  }

stopCluster(cl) # stop parallelizing 

saveRDS(models, ".\\batteries_noIIS.RDS")

```
