---
title: "time series analysis"
author: "Laura Menicacci"
date: "2023-12-05"
output: html_document
---

# Exploration Break detection

-   Controls: GDP and population
-   Data samples: Y02 (all ccmts), Y02E (energy), solar, wind, batteries
-   Total countries covered: 196

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gets)
library(getspanel)
library(here)
library(doParallel)
library(readxl)
library(gdata)
library(ggthemes)
library(collapse)
library(plm)
library(forecast)
library(tseries)
library(patchwork)
library(urca)
library(kableExtra)

df <- read_csv(".\\data\\PAT_DEV_MOD_SPEC.csv", show_col_types = F) 

df1 <- df %>% select(COU, `Inventor country`, `Technology domain`, Year, Value) %>% rename("ISO" = "COU", "country" = "Inventor country", "tech" = "Technology domain", "count" = "Value", "year" = "Year")

################# aggregate the solar technology counts together 

solar_list <- c("Solar thermal-PV hybrids", "Solar photovoltaic (PV) energy", "Solar thermal energy")

df1 <- df1 %>% 
  mutate(tech = case_when(tech %in% solar_list ~ "Solar energy",
    TRUE ~ as.character(tech))) %>%
  group_by(ISO, year, tech) %>%
  summarise(count = sum(count)) %>%
  ungroup()


```

## Prepare data

-   Aggregate 3 types of solar techs into 1
-   Add 0 values for missing years

```{r, echo=FALSE}
years <- 1990:2020

# Create a data frame with all combinations of countries, years, and tech types
expand_df <- expand.grid(ISO = unique(df1$ISO), year = years, tech = unique(df1$tech))
expand_df$count <- 0  # Initialize count column with 0

# Merge with the original data
merged_df <- merge(expand_df, df1, by = c("ISO", "year", "tech"), all.x = TRUE)

# Replace NA values in the count column with 0
merged_df$count.y[is.na(merged_df$count.y)] <- 0

df2 <- merged_df %>% select(ISO, year, tech, count.y) %>% rename("count" = "count.y")

```

## Restrict country sample

1. Group by country and technology class 

2. Create statistical info: median, q25, mean, q75, max sd

Example of how the dataset looks like:

- a lot of zeros!
```{r, echo=FALSE}
stats_pat <- df2 %>% 
  group_by(ISO, tech) %>% 
  summarise(median = median(count, na.rm=TRUE),
            q25 = quantile(count, 0.25),
            mean = mean(count, na.rm=TRUE), 
            q75 = quantile(count, 0.75), 
            max = max(count, na.rm=TRUE), 
            sd = sd(count, na.rm=TRUE), .groups = "keep")

stats_pat %>% 
  head(25) %>% 
  kable(format = "html") %>% 
  kable_styling(bootstrap_options = c("hover", "responsive"), full_width = F, fixed_thead = T, position = "left") %>% 
  scroll_box(width = "600px", height = "300px")

```

Whole distribution of country means faceted by technology: 
```{r, echo=FALSE, fig.height=10, fig.width=15}

box <- stats_pat %>% 
  ggplot(aes(x = mean))+ 
  geom_boxplot(colour = "black", outlier.colour = "red", size = 0.5) +
  facet_wrap(~tech, scales = "free") + 
  xlab("")+
  ylab("Mean counts by country") +
  theme_clean() +
  theme(plot.background = element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

hist <- stats_pat %>% 
  ggplot(aes(x = mean)) +
  geom_histogram(binwidth = 1, fill = "navy", colour = "black", alpha = 0.7) +
  facet_wrap(~tech, scales = "free") + 
  ylab("") +
  xlab("Mean counts by country (binwidth = 1)") +
  theme_clean() +
  theme(plot.background = element_blank())

box / hist

```

Divide distribution in quantiles and plot country 25th quantile faceted by technology: 

- where to cut the distribution?
- vertical red line on the 30th quantile

```{r, echo=FALSE, fig.height=12, fig.width=15}

box <- stats_pat %>% 
  ggplot(aes(x = q25))+ 
  geom_boxplot(colour = "black", outlier.colour = "red", size = 0.5) +
  geom_vline(xintercept = quantile(stats_pat$q25, 0.3), color = "red")+
  facet_wrap(~tech, scales = "free") + 
  ylab("")+
  xlab("Q25 counts by country") +
  theme_clean() +
  theme(plot.background = element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

hist <- stats_pat %>% 
  ggplot(aes(x = q25)) +
  geom_histogram(binwidth = 1, fill = "navy", colour = "black", alpha = 0.7) +
  geom_vline(xintercept = quantile(stats_pat$q25, 0.3), color = "red")+
  facet_wrap(~tech, scales = "free") + 
  ylab("") +
  xlab("Q25 of counts by country (binwidth = 1)") +
  theme_clean() +
  theme(plot.background = element_blank())

box / hist

```

3. **Selection criteria**: for each q25 of country&tech, if it is less than 30th quantile of entire distribution of patent counts, drop 

```{r, echo=FALSE, include=FALSE}
q30 <- quantile(df2$count, 0.30)

nonpat_q30 <- c() # 175


for (i in 1:nrow(stats_pat)){
  if (stats_pat[i, 4] <= q30[[1]]){ # if q25 of country&tech is less than q30 of entire distribution: drop
    nonpat_q30 <- append(nonpat_q30, stats_pat[[i, 1]]) 
                       }
}

df_strict <- df2 %>% filter(!(ISO %in% nonpat_q30))

```

4. Total sample: 21 countries 

Time series:
```{r, echo=FALSE, fig.height=17, fig.width=17}
df_strict %>% 
  #group_by(ISO, year, tech) %>%
  #summarise(tot = sum(count), .groups = "keep") %>% 
  ggplot(aes(y = count, x = year, colour = tech)) +
  geom_line(alpha = 0.7) +
  facet_wrap(~ISO, scales = "free") + 
  ylab("patent counts") +
  xlab("year") +
  ggtitle("Time series for restricted country sample") +
  theme_minimal() + theme(legend.position = "bottom")

```


Reasons:

* I wanted to make sure that all countries in the sample had a decent distribution for all the technologies for the first run of the model
* Keep sample small to make it run faster
* Double-checked with **top 25 patenting countries**: they are almost the same except for *Brazil, India, Taiwan, Singapore*, which then were added for the second run 

Check change in distribution:
```{r, fig.height=20, fig.width=15, echo=FALSE}
stats_pat_top <- df_strict %>% 
  group_by(ISO, tech) %>% 
  summarise(median = median(count, na.rm=TRUE),
            q25 = quantile(count, 0.25),
            mean = mean(count, na.rm=TRUE), 
            q75 = quantile(count, 0.75), 
            max = max(count, na.rm=TRUE), 
            sd = sd(count, na.rm=TRUE), 
            tot = sum(count, na.rm = TRUE), .groups = "keep")

box <- stats_pat_top %>% 
  ggplot(aes(x = mean))+ 
  geom_boxplot(colour = "black", outlier.colour = "red", size = 0.5) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red")+
  facet_wrap(~tech, scales = "free") + 
  xlab("")+
  ylab("mean patent counts by country") +
  theme_clean() +
  theme(plot.background = element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

hist <- stats_pat_top %>% 
  ggplot(aes(x = mean)) +
  geom_histogram(binwidth = 1, fill = "navy", colour = "black", alpha = 0.7) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red") +
  facet_wrap(~tech, scales = "free") + 
  ylab("") +
  xlab("mean patent counts by country (binwidth = 1)") +
  theme_clean() +
  theme(plot.background = element_blank())

#line <- df3 %>% 
#  group_by(tech, year) %>%
#  summarise(tot = sum(count), .groups = "keep") %>% 
#  ggplot(aes(y = tot, x = year)) +
#  geom_line(colour = "black", alpha = 0.7) +
#  facet_wrap(~tech, scales = "free") + 
#  ylab("aggregated patent counts by tech") +
#  xlab("year") +
#  theme_clean() +
#  theme(plot.background = element_blank())

box / hist 
```


**Alternative: Select 25 top patenting countries by mean**
- Check distribution of country means:
```{r, echo=FALSE, fig.height=20, fig.width=15}

stats_pat2 <- stats_pat[order(stats_pat$mean, decreasing = TRUE),]

top_pat_countries <- unique(stats_pat2[1:70, 1]) # top 25 patenting countries 

df3_25 <- df2 %>% filter(ISO %in% top_pat_countries$ISO)

#df3_25 %>% 
#  #group_by(ISO, year, tech) %>%
#  #summarise(tot = sum(count), .groups = "keep") %>% 
#  ggplot(aes(y = count, x = year, colour = tech)) +
#  geom_line(alpha = 0.7) +
#  facet_wrap(~ISO, scales = "free") + 
#  ylab("patent counts") +
#  xlab("year") +
#  theme_minimal() + theme(legend.position = "bottom")

stats_pat_top <- df3_25 %>% 
  group_by(ISO, tech) %>% 
  summarise(median = median(count, na.rm=TRUE),
            q25 = quantile(count, 0.25),
            mean = mean(count, na.rm=TRUE), 
            q75 = quantile(count, 0.75), 
            max = max(count, na.rm=TRUE), 
            sd = sd(count, na.rm=TRUE), 
            tot = sum(count, na.rm = TRUE), .groups = "keep")

box <- stats_pat_top %>% 
  ggplot(aes(x = mean))+ 
  geom_boxplot(colour = "black", outlier.colour = "red", size = 0.5) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red")+
  facet_wrap(~tech, scales = "free") + 
  xlab("")+
  ylab("mean patent counts by country") +
  theme_clean() +
  theme(plot.background = element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

hist <- stats_pat_top %>% 
  ggplot(aes(x = mean)) +
  geom_histogram(binwidth = 1, fill = "navy", colour = "black", alpha = 0.7) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red") +
  facet_wrap(~tech, scales = "free") + 
  ylab("") +
  xlab("mean patent counts by country (binwidth = 1)") +
  theme_clean() +
  theme(plot.background = element_blank())


box / hist
```

**Another alternative**: Select 50 top patenting countries (by mean) and check again distribution of country means:
```{r, echo=FALSE, fig.height=20, fig.width=15}

#stats_pat %>% 
#  group_by(tech) %>% 
#  arrange(desc(mean))

stats_pat2 <- stats_pat[order(stats_pat$mean, decreasing = TRUE),]

top_pat_countries <- unique(stats_pat2[1:156, 1]) # top 50 patenting countries 

df3 <- df2 %>% filter(ISO %in% top_pat_countries$ISO)

stats_pat_top <- df3 %>% 
  group_by(ISO, tech) %>% 
  summarise(median = median(count, na.rm=TRUE),
            q25 = quantile(count, 0.25),
            mean = mean(count, na.rm=TRUE), 
            q75 = quantile(count, 0.75), 
            max = max(count, na.rm=TRUE), 
            sd = sd(count, na.rm=TRUE), 
            tot = sum(count, na.rm = TRUE), .groups = "keep")

box <- stats_pat_top %>% 
  ggplot(aes(x = mean))+ 
  geom_boxplot(colour = "black", outlier.colour = "red", size = 0.5) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red")+
  facet_wrap(~tech, scales = "free") + 
  xlab("")+
  ylab("mean patent counts by country") +
  theme_clean() +
  theme(plot.background = element_blank(), 
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

hist <- stats_pat_top %>% 
  ggplot(aes(x = mean)) +
  geom_histogram(binwidth = 1, fill = "navy", colour = "black", alpha = 0.7) +
  #geom_vline(xintercept = quantile(stats_pat_top$mean, 0.3), color = "red") +
  facet_wrap(~tech, scales = "free") + 
  ylab("") +
  xlab("mean patent counts by country (binwidth = 1)") +
  theme_clean() +
  theme(plot.background = element_blank())

#line <- df3 %>% 
#  group_by(tech, year) %>%
#  summarise(tot = sum(count), .groups = "keep") %>% 
#  ggplot(aes(y = tot, x = year)) +
#  geom_line(colour = "black", alpha = 0.7) +
#  facet_wrap(~tech, scales = "free") + 
#  ylab("aggregated patent counts by tech") +
#  xlab("year") +
#  theme_clean() +
#  theme(plot.background = element_blank())

box / hist

```


## Time series analysis

**Augmented Dickey-Fuller Test** 

- Check for stationarity by technology
- Three types of tests

```{r}
adf_data_ccmt <- df3 %>% filter(tech == "Climate change mitigation")

adf_data_energy <- df3 %>% filter(tech == "Climate change mitigation technologies related to energy generation, transmission or distribution")

adf_data_batteries <- df3 %>% filter(tech == "Batteries")

adf_data_solar <- df3 %>% filter(tech == "Solar energy")

adf_data_wind <- df3 %>% filter(tech == "Wind energy")
```


### CCMT

```{r, echo=TRUE}

summary(ur.df(y=adf_data_ccmt$count, type = "none",lags=1))

summary(ur.df(y=adf_data_ccmt$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_ccmt$count, type = "trend",lags=1))

```


### ENERGY 

```{r}

summary(ur.df(y=adf_data_energy$count, type = "none",lags=1))

summary(ur.df(y=adf_data_energy$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_energy$count, type = "trend",lags=1))
```


### SOLAR
```{r}


summary(ur.df(y=adf_data_solar$count, type = "none",lags=1))

summary(ur.df(y=adf_data_solar$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_solar$count, type = "trend",lags=1))
```

### WIND
```{r}


summary(ur.df(y=adf_data_wind$count, type = "none",lags=1))

summary(ur.df(y=adf_data_wind$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_wind$count, type = "trend",lags=1))
```

### BATTERIES

```{r}


summary(ur.df(y=adf_data_batteries$count, type = "none",lags=1))

summary(ur.df(y=adf_data_batteries$count, type = "drift",lags=1))

summary(ur.df(y=adf_data_batteries$count, type = "trend",lags=1))
```