---
title: "Brown patents brief data analysis"
author: "Laura Menicacci"
date: "2024-03-22"
output: html_document
---

Source of the data: [IEA](https://www.iea.org/data-and-statistics/data-tools/energy-technology-patents-data-explorer). Double-checked via email with IEA people that these counts are comparable: fractional counts according to inventor’s countries of priority applications and of family size greater than two (PF2). Same as OECD ones!

```{r setup, echo=FALSE}

## libraries
suppressWarnings(suppressMessages(library(knitr)))
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(here)))

#here::i_am("sharing/brown_patents.R")

top_25 <- c("JPN", "USA", "KOR", "DEU", "CHN", "FRA", "GBR", "TWN", "CAN", "ITA", "DNK", "NLD", "IND", "AUT", "CHE", "SWE", "ESP", "AUS", "ISR", "BEL", "FIN", "RUS", "NOR", "SGP", "BRA")

df <- read.csv(here::here("data/patents_panel_5techs_spread.csv")) %>% 
  filter(ISO %in% top_25) %>% 
  filter(year < 2020 & year > 1999) %>% # cut time series 
  select(!count_batteries)

#df %>% filter(!complete.cases(.))

```

# Plot TOTAL distribution (without filtering for our country sample)

33 countries. 

NOTE: here SAUDI ARABIA (SAU) plays a role that we don't see in the clean patents (obviously)

```{r, fig.height=10, fig.width=10, echo=FALSE}
df1 <- read.csv(here::here("data/patents_panel_5techs_spread.csv")) %>% 
  #filter(ISO %in% top_25) %>% 
  filter(year < 2020 & year > 1999) %>% # cut time series 
  select(!count_batteries) %>% 
  drop_na() 

df1 %>% 
  ggplot(aes(x = brown_patents)) +
  geom_boxplot() +
  facet_wrap(~ISO, scales = "free") +
  theme_bw() #+
  #scale_x_continuous(limits = c(0, 1000))
```


# Plot time series for top 25 countries against the ccmt faceted by country

In general CCMT patenting seems to be more than brown in all the countries in our sample, energy is more aligned with the trend of the brown.  
```{r, fig.width=10, fig.height=10, echo=FALSE}
df %>%
  #filter(ISO == "SAU") %>%
  ggplot(aes(y = brown_patents, x = year)) +
  geom_line(aes(colour = "brown patents")) +
  geom_line(aes(y = count_ccmt, colour = "green patents")) +
  geom_line(aes(y = count_energy, colour = "energy patents")) +
  facet_wrap(~ISO, scales = "free") +
  scale_colour_manual(values = c("brown patents" = "brown", 
                                  "green patents" = "green",
                                  "energy patents" = "yellow")) +
  theme_bw()

```

# comparison brown vs solar and wind 

USA super interesting: after 2010s brown takes over and the solar and wind diminishes! supports hydrofracking hypothesis (moreover numbers dominate the whole sample)
```{r, fig.width=10, fig.height=10, echo=FALSE}
df %>%
  #filter(ISO == "SAU") %>%
  ggplot(aes(y = brown_patents, x = year)) +
  geom_line(aes(colour = "brown patents")) +
  geom_line(aes(y = count_wind, colour = "wind patents")) +
  geom_line(aes(y = count_solar, colour = "solar patents")) +
  facet_wrap(~ISO, scales = "free") +
  scale_colour_manual(values = c("brown patents" = "brown", 
                                  "solar patents" = "orange",
                                  "wind patents" = "lightblue")) +
  theme_bw()

```

# Plot ccmt against brown

interesting: CANADA and USA the relationship seems logarithmic? what does it mean? 
Australia? negative association
```{r, fig.height=10, fig.width=10, echo=FALSE}
df %>% 
  ggplot(aes(x = brown_patents, y = count_ccmt)) +
  geom_point()+
  geom_smooth(method = "lm", se = TRUE, alpha = 0.3, colour = 'red', fill = 'lightgrey') +
  facet_wrap(~ISO, scales = "free")+
  theme_bw()
```

# Plot energy against brown

```{r, fig.height=10, fig.width=10, echo=FALSE}
df %>% 
  ggplot(aes(x = brown_patents, y = count_energy)) +
  geom_point()+
  geom_smooth(method = "lm", se = TRUE, alpha = 0.3, colour = 'red', fill = 'lightgrey') +
  facet_wrap(~ISO, scales = "free")+
  theme_bw()

```
 
 