---
title: "sc_replication_09_01"
author: "Laura Menicacci"
date: "2024-01-09"
output: html_document
---

# Generalised synthetic controls replication {.tabset}

Results refer to the following specification: 

 * Y: Log count +1
 * Controls: lgdp + lpop
 * Sample: top 25 patenting countries by mean
 * AR(1)
 * IIS = ON
 * p-value = 0.01 (very strict)

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load Libraries
suppressWarnings(suppressMessages(library(knitr)))
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(gsynth)))
suppressWarnings(suppressMessages(library(panelView)))
suppressWarnings(suppressMessages(library(patchwork)))
suppressWarnings(suppressMessages(library(gets)))
suppressWarnings(suppressMessages(library(getspanel)))
suppressWarnings(suppressMessages(library(kableExtra)))

# Load plotting functions
source(".\\breaks_comparison_functions.R")

top_25 <- c("JPN", "USA", "KOR", "DEU", "CHN", "FRA", "GBR", "TWN", "CAN", "ITA", "DNK", "NLD", "IND", "AUT", "CHE", "SWE", "ESP", "AUS", "ISR", "BEL", "FIN", "RUS", "NOR", "SGP", "BRA")

# Load Data
#data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = #F) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% #mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop))
#
# Load results 
ccmt <- readRDS(".\\ccmt_09_01_24_sample_exp.RDS") %>% mutate(tech = "ccmt")
energy <- readRDS(".\\energy_09_01_24_sample_exp.RDS") %>% mutate(tech = "energy")
solar <- readRDS(".\\solar_09_01_24_sample_exp.RDS") %>% mutate(tech = "solar")
wind <- readRDS(".\\wind_09_01_24_sample_exp.RDS") %>% mutate(tech = "wind")
batteries <- readRDS(".\\batteries_09_01_24_sample_exp.RDS") %>% mutate(tech = "batteries")

results <- rbind(ccmt, energy, solar, wind, batteries)

# Extract breaks list

## for preferred spec: top_25 and log transformation 
res_w_breaks <- readRDS(".\\prefe_results_w_breaks_list_09_01.RDS")

#all_res_w_breaks <- find_breaks(results) NON HA FUNZIONATO
#saveRDS(all_res_w_breaks, ".\\all_res_breaks_09_01.RDS")


# Find common breaks
#common_breaks_prefe <- filter_for_common_breaks(res_w_breaks)

common_breaks_prefe <- readRDS(".\\prefe_spec_common_breaks.RDS")
#saveRDS(common_breaks_prefe, ".\\prefe_spec_common_breaks.RDS")

```

## CCMT {.tabset}

Countries with treatment before 2000 cannot be estimated (India). 

List of breaks:

```{r, echo=FALSE}
data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = F, col_names = T) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop)) %>% filter(tech == "Climate change mitigation")
# list of breaks for ccmt

res_w_breaks %>% 
  filter(tech == "ccmt" & p_val == 0.01) %>% 
  pull(breaks)

# Create Staggered SCM Treatments with list of breaks

data$treated <- 0

# pval 0.01
data$treated <- ifelse(data$ISO == "AUS" & data$year >= 2005, 1, data$treated)
data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2005, 1, data$treated)
#data$treated <- ifelse(data$ISO == "IND" & data$year >= 1998, 1, data$treated)
data$treated <- ifelse(data$ISO == "IND" & data$year >= 2000, 1, data$treated)
data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2003, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2005, 1, data$treated)

# pval 0.05
#data$treated <- ifelse(data$ISO == "AUS" & data$year >= 2005, 1, data$treated)
#data$treated <- ifelse(data$ISO == "CAN" & data$year >= 1997, 1, data$treated)
#data$treated <- ifelse(data$ISO == "CHN" & data$year >= 2001, 1, data$treated)
##data$treated <- ifelse(data$ISO == "CHN" & data$year >= 2015, 1, data$treated)
#data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2005, 1, data$treated)
##data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2006, 1, data$treated)
##data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2007, 1, data$treated)
#data$treated <- ifelse(data$ISO == "IND" & data$year >= 1998, 1, data$treated)
##data$treated <- ifelse(data$ISO == "IND" & data$year >= 2000, 1, data$treated)
#data$treated <- ifelse(data$ISO == "ISR" & data$year >= 2009, 1, data$treated)
#data$treated <- ifelse(data$ISO == "RUS" & data$year >= 1998, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2003, 1, data$treated)
##data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2005, 1, data$treated)
#data$treated <- ifelse(data$ISO == "TWN" & data$year >= 2001, 1, data$treated)


```


```{r ccmt, echo=FALSE}

# Check Treatments
v1 <- panelview(count ~ treated, data = data,  
          index = c("ISO","year"), 
          pre.post = TRUE,
          axis.adjust = TRUE,
          cex.axis.y = 8, 
          cex.legend = 8, 
          background = "white") 

# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "parametric", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)

#saveRDS(out, file = ".\\gsynth_ccmt.RDS")

```


### Positive {.tabset}


```{r ccmt-plot-pos, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt.RDS")

plot(out, type = "gap", id = "DNK", main = "Denmark 2005 (Climate change mitigation)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2005 (Climate change mitigation)")

plot(out, type = "gap", id = "IND", main = "India 2000 (Climate change mitigation)")
plot(out, type = "ct", id = "IND", main = "India 2000 (Climate change mitigation)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2003 (Climate change mitigation)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2003 (Climate change mitigation)")

```


### Negative {.tabset}


```{r ccmt-plot-neg, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_ccmt.RDS")

plot(out, type = "gap", id = "AUS", main = "Australia 2005 (Climate change mitigation)")
plot(out, type = "ct", id = "AUS", main = "Australia 2005 (Climate change mitigation)")

```



## ENERGY {.tabset}

Countries with treatment before 2000 cannot be estimated (India, Belgium, Sweden)

```{r energy, echo=FALSE}

data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = F) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop)) %>% filter(tech == "Climate change mitigation technologies related to energy generation, transmission or distribution")
# list of breaks for ccmt

res_w_breaks %>% 
  filter(tech == "energy" & p_val == 0.01) %>% 
  pull(breaks)

# Create Staggered SCM Treatments
data$treated <- 0

#data$treated <- ifelse(data$ISO == "BEL" & data$year >= 1997, 1, data$treated)
data$treated <- ifelse(data$ISO == "BRA" & data$year >= 2014, 1, data$treated)
data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2005, 1, data$treated)
#data$treated <- ifelse(data$ISO == "IND" & data$year >= 1998, 1, data$treated)
data$treated <- ifelse(data$ISO == "IND" & data$year >= 2001, 1, data$treated)
data$treated <- ifelse(data$ISO == "RUS" & data$year >= 2007, 1, data$treated)
data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2001, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2003, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2010, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SWE" & data$year >= 1998, 1, data$treated)

# Check Treatments
v1 <- panelview(count ~ treated, data = data,  
          index = c("ISO","year"), 
          pre.post = TRUE,
          axis.adjust = TRUE,
          cex.axis.y = 8, 
          cex.legend = 8, 
          background = "white") 

# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "parametric", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)

#saveRDS(out, file = ".\\gsynth_energy.RDS")

```



### Positive {.tabset}


```{r energy-plot-pos, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_energy.RDS")

#plot(out, type = "gap", id = "BEL", main = "Belgium 1997 (energy)")
#plot(out, type = "ct", id = "BEL", main = "Belgium 1997 (energy)")

plot(out, type = "gap", id = "BRA", main = "Brasil 2014 (energy)")
plot(out, type = "ct", id = "BRA", main = "Brasil 2014 (energy)")

plot(out, type = "gap", id = "DNK", main = "Denmark 2005 (energy)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2005 (energy)")

plot(out, type = "gap", id = "IND", main = "India 2001 (energy)")
plot(out, type = "ct", id = "IND", main = "India 2001 (energy)")

plot(out, type = "gap", id = "RUS", main = "Russia 2007 (energy)")
plot(out, type = "ct", id = "RUS", main = "Russia 2007 (energy)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2001 (energy)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2001 (energy)")


```

### Negative {.tabset}

```{r energy-plot-neg, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_energy.RDS")

plot(out, type = "gap", id = "RUS", main = "Russia 2007 (energy)")
plot(out, type = "ct", id = "RUS", main = "Russia 2007 (energy)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2001 (energy)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2001 (energy)")


```


## SOLAR {.tabset}

Countries with treatment before 2000 cannot be estimated (The Netherlands)

```{r solar, echo=FALSE}

data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = F) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop)) %>% filter(tech == "Solar energy")

# list of breaks for ccmt

res_w_breaks %>% 
  filter(tech == "solar" & p_val == 0.01) %>% 
  pull(breaks)

# Create Staggered SCM Treatments
data$treated <- 0
data$treated <- ifelse(data$ISO == "AUS" & data$year >= 2005, 1, data$treated)
data$treated <- ifelse(data$ISO == "BRA" & data$year >= 2014, 1, data$treated)
data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2001, 1, data$treated)
data$treated <- ifelse(data$ISO == "KOR" & data$year >= 2003, 1, data$treated)
#data$treated <- ifelse(data$ISO == "NLD" & data$year >= 1997, 1, data$treated)
data$treated <- ifelse(data$ISO == "RUS" & data$year >= 2004, 1, data$treated)
data$treated <- ifelse(data$ISO == "SWE" & data$year >= 2001, 1, data$treated)
data$treated <- ifelse(data$ISO == "TWN" & data$year >= 2005, 1, data$treated)


# Check Treatments
v1 <- panelview(count ~ treated, data = data,  
          index = c("ISO","year"), 
          pre.post = TRUE,
          axis.adjust = TRUE,
          cex.axis.y = 8, 
          cex.legend = 8, 
          background = "white") 

# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "parametric", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)
#
#saveRDS(out, file = ".\\gsynth_solar.RDS")

```


### Positive {.tabset}


```{r solar-plot-pos, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_solar.RDS")

plot(out, type = "gap", id = "BRA", main = "Brasil 2014 (solar)")
plot(out, type = "ct", id = "BRA", main = "Brasil 2014 (solar)")

plot(out, type = "gap", id = "DNK", main = "Denmark 2001 (solar)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2001 (solar)")

plot(out, type = "gap", id = "KOR", main = "Korea 2003 (solar)")
plot(out, type = "ct", id = "KOR", main = "Korea 2003 (solar)")

plot(out, type = "gap", id = "TWN", main = "Taiwan 2005 (solar)")
plot(out, type = "ct", id = "TWN", main = "Taiwan 2005 (solar)")

```


### Negative {.tabset}

```{r solar-plot-neg, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_solar.RDS")

plot(out, type = "gap", id = "AUS", main = "Australia 2005 (solar)")
plot(out, type = "ct", id = "AUS", main = "Australia 2005 (solar)")

plot(out, type = "gap", id = "RUS", main = "Russia 2004 (solar)")
plot(out, type = "ct", id = "RUS", main = "Russia 2004 (solar)")

plot(out, type = "gap", id = "SWE", main = "Sweden 2001 (solar)")
plot(out, type = "ct", id = "SWE", main = "Sweden 2001 (solar)")

```

## WIND {.tabset}

Countries with treatment before 2000 cannot be estimated (Japan)

```{r wind, echo=FALSE}

data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = F) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop)) %>% filter(tech == "Wind energy")

# list of breaks for wind

res_w_breaks %>% 
  filter(tech == "wind" & p_val == 0.01) %>% 
  pull(breaks)

# Create Staggered SCM Treatments
data$treated <- 0
data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2006, 1, data$treated)
#data$treated <- ifelse(data$ISO == "JPN" & data$year >= 1999, 1, data$treated)
data$treated <- ifelse(data$ISO == "RUS" & data$year >= 2003, 1, data$treated)
data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2007, 1, data$treated)
#data$treated <- ifelse(data$ISO == "SGP" & data$year >= 2012, 1, data$treated)
data$treated <- ifelse(data$ISO == "SWE" & data$year >= 2002, 1, data$treated)

# Check Treatments
v1 <- panelview(count ~ treated, data = data,  
          index = c("ISO","year"), 
          pre.post = TRUE,
          axis.adjust = TRUE,
          cex.axis.y = 8, 
          cex.legend = 8, 
          background = "white") 

# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(lcount ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "parametric", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)
#
#saveRDS(out, file = ".\\gsynth_wind.RDS")

```



### Positive {.tabset}

```{r wind-plot-pos, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_wind.RDS")

plot(out, type = "gap", id = "DNK", main = "Denmark 2006 (wind)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2006 (wind)")

plot(out, type = "gap", id = "SGP", main = "Singapore 2007 (wind)")
plot(out, type = "ct", id = "SGP", main = "Singapore 2007 (wind)")


```

### Negative {.tabset}

```{r wind-plot-neg, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_wind.RDS")


plot(out, type = "gap", id = "RUS", main = "Russia 2003 (wind)")
plot(out, type = "ct", id = "RUS", main = "Russia 2003 (wind)")

plot(out, type = "gap", id = "SWE", main = "Sweden 2002 (wind)")
plot(out, type = "ct", id = "SWE", main = "Sweden 2002 (wind)")



```


## BATTERIES {.tabset}

```{r batteries, echo=FALSE}

data <- read_csv(".\\data\\patents_panel_5techs.csv", show_col_types = F) %>% filter(ISO %in% top_25 & year > 1994 & year < 2020) %>% mutate(lcount = log(count+1), lgdp = log(gdp), lpop = log(pop)) %>% filter(tech == "Batteries")

# list of breaks for batteries

res_w_breaks %>% 
  filter(tech == "batteries" & p_val == 0.01) %>% 
  pull(breaks)

# Create Staggered SCM Treatments
data$treated <- 0
data$treated <- ifelse(data$ISO == "AUT" & data$year >= 2009, 1, data$treated)
data$treated <- ifelse(data$ISO == "BRA" & data$year >= 2010, 1, data$treated)
#data$treated <- ifelse(data$ISO == "BRA" & data$year >= 2015, 1, data$treated)
data$treated <- ifelse(data$ISO == "DNK" & data$year >= 2001, 1, data$treated)
data$treated <- ifelse(data$ISO == "NLD" & data$year >= 2007, 1, data$treated)
data$treated <- ifelse(data$ISO == "RUS" & data$year >= 2007, 1, data$treated)
#data$treated <- ifelse(data$ISO == "RUS" & data$year >= 2015, 1, data$treated)
data$treated <- ifelse(data$ISO == "TWN" & data$year >= 2001, 1, data$treated)

# Check Treatments
v1 <- panelview(count ~ treated, data = data,  
          index = c("ISO","year"), 
          pre.post = TRUE,
          axis.adjust = TRUE,
          cex.axis.y = 8, 
          cex.legend = 8, 
          background = "white") 

# Run Gsynth with Staggered Treatments (IFE)
#system.time(
#  out <- gsynth(count ~ treated 
#                 + lgdp + lpop,
#                data = data, 
#                index = c("ISO","year"), force = "two-way", 
#                CV = TRUE, r = c(0, 3), se = TRUE, 
#                inference = "parametric", nboots = 1000, 
#                parallel = FALSE, estimator = "ife")
#)
#
#saveRDS(out, file = ".\\gsynth_batteries.RDS")

```

### Positive {.tabset}

```{r batteries-plot-pos, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_batteries.RDS")

plot(out, type = "gap", id = "AUT", main = "Austria 2009 (batteries)")
plot(out, type = "ct", id = "AUT", main = "Austria 2009 (batteries)")

plot(out, type = "gap", id = "TWN", main = "Taiwan 2001 (batteries)")
plot(out, type = "ct", id = "TWN", main = "Taiwan 2001 (batteries)")

```

### Negative {.tabset}

```{r batteries-plot-neg, echo=FALSE, fig.show="hold", out.width="50%"}

out <- readRDS(".\\gsynth_batteries.RDS")

plot(out, type = "gap", id = "BRA", main = "Brasil 2010 (batteries)")
plot(out, type = "ct", id = "BRA", main = "Brasil 2010 (batteries)")

plot(out, type = "gap", id = "DNK", main = "Denmark 2001 (batteries)")
plot(out, type = "ct", id = "DNK", main = "Denmark 2001 (batteries)")

plot(out, type = "gap", id = "NLD", main = "The Netherlands 2007 (batteries)")
plot(out, type = "ct", id = "NLD", main = "The Netherlands 2007 (batteries)")

plot(out, type = "gap", id = "RUS", main = "Russia 2007 (batteries)")
plot(out, type = "ct", id = "RUS", main = "Russia 2007 (batteries)")

```


# Common breaks across technologies and specifications {.tabset}

```{r, echo=FALSE}
common_breaks_prefe %>% 
  #filter(source == "log_count~ lgdp + lpop") %>% 
  select(source, p_val, tech, break_year, break_ISO) %>% 
  group_by(break_ISO) %>% 
  kable(format = "html") %>% 
  kable_styling(bootstrap_options = c("hover", "responsive"), full_width = F, fixed_thead = T, position = "left") %>% 
  scroll_box(width = "600px", height = "300px")
  
```

